News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-03-24 rupnik2015.tex

The details of the first step are described in Algorithm~\ref{cluster_merge_algo1}. The algorithm begins by individually inspecting each article $a_i$ in the cluster $c_i$. Using a chosen method for computing cross-lingual document similarity (see Section~\ref{sec:models}), it identifies the 10 most similar articles to $a_i$ in each language $l \in L$. For each  similar article $a_j$, we identify its corresponding  cluster $c_j$ and add it to the set of candidates. The set of candidate clusters obtained in this way is several orders of magnitude smaller than the number of all clusters. Although computed document similarities are approximate, our  assumption  is that articles in different languages describing the same event, will generally have a higher similarity than articles about different events. While this assumption does not always hold, redundancy in the data mitigates these false positives. Since we compute the 10 most similar articles for each article in $c_i$, we are likely to identify all the relevant candidates for cluster $c_i$.

>>>>

The details of the first step are described in Algorithm~\ref{cluster_merge_algo1}. The algorithm begins by individually inspecting each article $a_i$ in the cluster $c_i$. Using a cross-lingual document similarity measure (see Section~\ref{}), it identifies the 10 most similar articles to $a_i$ in each language $l \in L$. For each  similar article $a_j$, we identify its corresponding  cluster $c_j$ and add it to the set of candidates. The set of candidate clusters obtained in this way is several orders of magnitude smaller than the number of all clusters. Although computed document similarities are approximate, our  assumption  is that articles in different languages describing the same event, will generally have a higher similarity than articles about different events. While this assumption does not always hold, redundancy in the data mitigates these false positives. Since we compute the 10 most similar articles for each article in $c_i$, we are likely to identify all the relevant candidates for cluster $c_i$.
